True versus apparent shapes of bow shocks and bow waves

### 2017-11-18 papers/Paper1/app-dust-equations.tex
Try to get projection working for divergent dragoids
But it doesn't work at the moment.
Re-run the dragoid dynamic models with much higher resolution
This now looks a lot better.  Also, use lowess smoothing on the
inclination tracks for dragoids

Equations~\eqref{eq:dust-motion} are integrated

>>>>

Equations~\eqref{eq:dust-motion} are integrated using the python
wrapper \texttt{scipy.integrate.odeint} to the Fortran ODEPACK library
\citep{Hindmarsh:1983a, Jones:2001a}, with results shown in
Figure~\ref{fig:dust-wave-coupling} for parallel-stream cases and
Figure~\ref{fig:divergent-dragoids} for divergent-stream cases.

### 2017-11-18 papers/Paper1/app-dust-wave.tex
Try to get projection working for divergent dragoids
But it doesn't work at the moment.
Re-run the dragoid dynamic models with much higher resolution
This now looks a lot better.  Also, use lowess smoothing on the
inclination tracks for dragoids

However, this description only applies to grains with impact
parameter, \(b\), that is exactly zero.  Even a very small finite
\(b\) means that \(\frad\) has a component perpendicular to the axis,
which pushes the grain to the side and means that, after re-coupling,
its second approach is at a much larger impact parameter than its
first, so it is dragged around the wings of the bow wave before it can
bounce in and out more than twice.  This is illustrated in
Figure~\ref{fig:dust-wave-coupling}, which shows grain trajectories
and the resulting dust density structure, calculated from numerical
integration of equations~\eqref{eq:dust-rad-force}
and~\eqref{eq:dust-fdrag} in 2-D cylindrical coordinates.  Results are
shown for a range of coupling parameters, \(\alpha\drag\).  The
\(\alpha\drag = 0.25\) case appears qualitatively similar to the no-drag
case shown in Figure~\ref{fig:dust-trajectories}a, except that the
inner edge of the bow wave has been shifted to a smaller radius.
Recoupling of the outgoing streamlines to the gas flow does occur
eventually, but on length scales larger than shown in the figure. The
\(\alpha\drag = 0.5\) case shows the oscillating trajectories discussed
above for those grains that come in with a small initial impact
parameter.  In the \(\alpha\drag = 1.0\) case, the oscillating trajectories
are more confined, forming a thick shell around \(R_0\).  In the
\(\alpha\drag = 2.0\) case, the shell is much thinner and concentrated at
the inner rim.  As \(\alpha\drag\) increases, the oscillations are damped
further so that the stagnation radius \(R_0 / \alpha\drag\) becomes a good
approximation to the apex radius of the density wave.  All the cases
illustrated are for a parallel incident stream, but a divergent stream
gives qualitatively similar behavior.  We propose the term
\textit{dragoid} for the 3-dimensional shapes of the bow waves, found
by rotating results such as Figure~\ref{fig:dust-wave-coupling} about
the symmetry axis.

@@

\section{Apparent shapes of projected dragoids}
\label{sec:dust-wave-apparent}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_dragoid}
  \caption{Plane-of-sky shapes for dragoids.}
  \label{fig:dragoid-xy-prime}
\end{figure}

>>>>

However, this description only applies to grains with impact
parameter, \(b\), that is exactly zero.  Even a very small finite
\(b\) means that \(\frad\) has a component perpendicular to the axis,
which pushes the grain to the side and means that, after re-coupling,
its second approach is at a much larger impact parameter than its
first, so it is dragged around the wings of the bow wave before it can
bounce in and out more than twice.  This is illustrated in
Figure~\ref{fig:dust-wave-coupling}, which shows grain trajectories
and the resulting dust density structure, calculated from numerical
integration of equations~\eqref{eq:dust-rad-force}
and~\eqref{eq:dust-fdrag} in 2-D cylindrical coordinates.  Results are
shown for a range of coupling parameters, \(\alpha\drag\).  The
\(\alpha\drag = 0.25\) case appears qualitatively similar to the no-drag
case shown in Figure~\ref{fig:dust-trajectories}a, except that the
inner edge of the bow wave has been shifted to a smaller radius.
Recoupling of the outgoing streamlines to the gas flow does occur
eventually, but on length scales larger than shown in the figure. The
\(\alpha\drag = 0.5\) case shows the oscillating trajectories discussed
above for those grains that come in with a small initial impact
parameter.  In the \(\alpha\drag = 1.0\) case, the oscillating trajectories
are more confined, forming a thick shell around \(R_0\).  In the
\(\alpha\drag = 2.0\) case, the shell is much thinner and concentrated at
the inner rim.  As \(\alpha\drag\) increases, the oscillations are damped
further so that the stagnation radius \(R_0 / \alpha\drag\) becomes a good
approximation to the apex radius of the density wave.  All the cases
illustrated are for a parallel incident stream, but a divergent stream
gives qualitatively similar behavior, as shown in
Appendix~\ref{sec:equat-moti-grains}.  We propose the term
\textit{dragoid} for the 3-dimensional shapes of the bow waves, found
by rotating results such as Figure~\ref{fig:dust-wave-coupling} about
the symmetry axis.

@@

\subsection{Apparent shapes of projected dragoids}
\label{sec:dust-wave-apparent}

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_dragoid}
  \caption{Plane-of-sky shapes for parallel-stream dragoids.}
  \label{fig:dragoid-xy-prime}
\end{figure}
\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{figs/test_xyprime_div_dragoid}
  \caption{Plane-of-sky shapes for divergent-stream dragoids.}
  \label{fig:dragoid-div-xy-prime}
\end{figure}
